The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-08-07 paper2_JNLS/paper.tex
NM

Though once dismissed as sailor's tales, rogue waves are now recognized as a real and present threat to naval structures (cite). These abnormally large waves are inherently tied to emergence of non-Gaussian statistics in the sea surface.

%Introduce waves. \\
Introduce papers: PRF, PNAS, and J Stat Phys. \\

The purpose of this manuscript is to:
\begin{itemize}
\item Provide a more comprehensive treatment of the experiments and theory in combination. In particular, we make new comparisons between theory and experiments, which further confirm the predictive power of the theoretical framework.
\item Provide more thorough treatment of the link between physical system parameters and model parameters. This will elucidate the connection between theory and experiments. In particular, we flesh out details of non-dimensionalization, which were only briefly discussed in \cite{majda2019statistical} for the sake of brevity.
\item Provide additional experimental measurements not presented in \cite{bolles2019anomalous}. For example, statistics on surface slope and autocorrelation.
\end{itemize}

@@

The evolution of any functional $\mathcal{F}[u]$ is given by 
\begin{align}
\partial_t \mathcal{F} = \{ \mathcal{F}, \Ham \} = \int_{-\pi}^{\pi} \vard{\mathcal{F}}{u} \sympJ \vard{\Ham}{u} \dx
\end{align}
where again $\Ham = \Hup$ if $t<0$ and $\Ham = \Hdn$ if $t>0$ and $\{\}$ is the Poisson bracket induced by $\sympJ$.

>>>>

Rogue waves are abnormally large surface waves, defined by oceanographers as those that exceed twice the significant wave height. Though such waves were once dismissed as myth, they have now been recorded in oceans across the globe and pose a recognized threat to seagoing vessels and naval structures. Rogue waves, also variously known as freak or anomalous waves, have been observed both in deep and shallow water, and can be triggered by a variety of mechanisms, including anomalous wind-forcing, focusing due to variable bathymetry, and a deep-water modulational instability that goes by the name Benjamin-Feir. The common tie between these mechanisms is their ability to generate non-normal statistics in the surface displacement; i.e.~When governed by Gaussian statistics, the likelihood of a rogue wave is extremely low, but these rare events can become much more common when statistics deviate from Gaussian.

A recent series of laboratory \cite{bolles2019anomalous} and numerical investigations \cite{viotti2014} have demonstrated the emergence of anomalous wave statistics from variations in bottom topography.

% Since studies are 1D topography, they offer bare minimum set of conditions able to generate anomalous waves; offers paradigm problem that can be studied scrutinized; shares features with more complex situations.

% ideal, paradigm, canonical

\vsp{4}
%Introduce waves. \\
Introduce papers: PRF, PNAS, and J Stat Phys. \\

The purpose of this manuscript is to:
\begin{itemize}
\item Provide a more comprehensive treatment of the experiments and theory in combination. In particular, we make new comparisons between theory and experiments, which further confirm the predictive power of the theoretical framework.
\item Provide more thorough treatment of the link between physical system parameters and model parameters. This will elucidate the connection between theory and experiments. In particular, we flesh out details of non-dimensionalization, which were only briefly discussed in \cite{majda2019statistical} for the sake of brevity.
%more transparent connection to experimental parameters
\item Provide additional experimental measurements not presented in \cite{bolles2019anomalous}. For example, statistics on surface slope and autocorrelation.
\end{itemize}

@@

The evolution of any functional $\mathcal{F}[u]$ is given by 
\begin{align}
\partial_t \mathcal{F} = \{ \mathcal{F}, \Ham \} = \int_{-\pi}^{\pi} \vard{\mathcal{F}}{u} \sympJ \vard{\Ham}{u} \dx
\end{align}
where again $\Ham = \Hup$ if $t<0$, and $\Ham = \Hdn$ if $t>0$ and $\{\}$ is the Poisson bracket induced by $\sympJ$.
